Molecular transport in human pial perivasculature

### 2024-11-13 paper/supplementary_main.tex
More updates in Supplementary, describe bifurcation conditions.

The concentration $\hat{c} = \hat{c}(s, t)$ in the periarterial and
perivenous networks ($s \in \Lambda_a, s \in \Lambda_v$), entering
in~\eqref{eq:3d_pde}, represents the concentration in the perivascular
space averaged over each perivascular cross-section and is governed by 
\begin{equation}
  \partial_t (A  \hat c) - \partial_s(\hat D A \partial_s ( \hat c)) +\partial_s(A \hat u \hat c )  +  \xi P (\hat c - \overline{c}) = 0
  \qquad \text{in} \quad \Lambda_a, \Lambda_v ,
\label{eq:1d_pde}
\end{equation}
where in $\Lambda_a, \Lambda_v$ refers to in each $\Lambda^i$ in each
of these networks. In~\eqref{eq:1d_pde}, $A = A(s)$ is defined as the
PVS cross-sectional area; i.e.,~for each $s \in \Lambda^i$ with
associated PVS $\Omega^i$, the area of the cross-section
$\Theta^i(s)$. Also, $\hat{D}$ is the effective diffusion coefficient,
and $\hat{u}$ is a convective velocity representing an (average) CSF
flow velocity in the axial direction of the perivascular spaces. To
complete~\eqref{eq:1d_pde}, we prescribe bifurcation conditions at
internal nodes of the perivascular networks $\Lambda_a, \Lambda_v$ and
boundary conditions at the end nodes. To this end, define the set of
internal nodes $\mathcal{B} \subset \mathcal{V}$ as the set of nodes
that are connected to two or more edges and the set of end nodes as
$\mathcal{T}$, write $\hat{c}_i = \hat{c}|_{\Lambda^i}$, and let
$\mathcal{E}(y)$ denote the set of (one, two or three) edges in
$\{\Lambda^i\}$ sharing the node $y$. To impose continuity of the
concentrations, we set that the concentrations when viewed from each
edge must match at nodes:
\begin{equation}
  \hat{c}_i (y) = \hat{c}_y \qquad \foralls \Lambda^i \in \mathcal{E}(y),
  \quad \foralls y \in \mathcal{B} .
\end{equation}
Moreover, to ensure conservation of flux, we set that the flux going
in and out at nodes should add to zero, or more precisely, that for
each $y \in \mathcal{B}$:
\begin{equation}
  \sum_{i \in \mathcal{E}(y)} (\hat{D} A_i \partial_s \hat{c}_i (y)  -  A_i \hat u_i(\mathsf{v}) \hat c_i(\mathsf{v})) n_i(\mathsf{v}) = 0
  \label{eq:flux_conservation}
\end{equation}

For a given edge $\Lambda^i= (\mathsf{v}_\mathrm{in}^i, \mathsf{v}_{\mathrm{out}}^{i})$, we define the function $n_i: \mathcal{V} \rightarrow \{-1,0,1\}$ with $$
n_i(\mathsf{v}_{\mathrm{in}}^i) = 1 , \,\, n _i (\mathsf{v}_{\mathrm{out}}^i) = -1 \,\, \mathrm{and} \,\,\, n_i(\mathsf{v}) = 0, \quad \forall \mathsf{v} \in 
\mathcal{V} \,  \backslash \,  \{ \mathsf{v}_{\mathrm{in}}^\mathsf e,\mathsf{v}_{\mathrm{out}}^\mathsf e \}.  
$$
The collection of bifurcation points is denoted by $\mathcal{B} = \{ \mathsf{v} \in \mathcal{V}, \,\,  \mathrm{card}(\mathcal{E}(\mathsf{v})) \geq  3\}$. For any $\mathsf{v} \in \mathcal{B}$, we have 
\begin{equation}
\sum_{ i \in \mathcal{E}(\mathsf{v})} (\hat D A_i \phi \partial_s \hat{u}_i(\mathsf{v})  -  A_i \hat u_i(\mathsf{v}) \hat c_i(\mathsf{v})) n_i(\mathsf{v}) = 0  \label{eq:flux_conservation}
\end{equation}

@@

\paragraph*{Interface conditions}

>>>>

The concentration $\hat{c} = \hat{c}(s, t)$ in the periarterial and
perivenous networks ($s \in \Lambda_a, s \in \Lambda_v$), entering
in~\eqref{eq:3d_pde}, represents the concentration in the perivascular
space averaged over each perivascular cross-section and is governed by 
\begin{equation}
  \partial_t (A  \hat c) - \partial_s( \hat D A \partial_s (\hat c) ) + \partial_s(A \hat u \hat c )  +  \xi P (\hat c - \overline{c}) = 0
  \qquad \text{in} \quad \Lambda_a, \Lambda_v ,
\label{eq:1d_pde}
\end{equation}
where in $\Lambda_a, \Lambda_v$ refers to in each $\Lambda^i$ in each
of these networks. In~\eqref{eq:1d_pde}, $A = A(s)$ is defined as the
PVS cross-sectional area; i.e.,~for each $s \in \Lambda^i$ with
associated PVS $\Omega^i$, the area of the cross-section
$\Theta^i(s)$. Also, $\hat{D}$ is the effective diffusion coefficient,
and $\hat{u}$ is a convective velocity representing an (average) CSF
flow velocity in the axial direction of the perivascular spaces. To
complete~\eqref{eq:1d_pde}, we prescribe bifurcation conditions at
internal nodes of the perivascular networks $\Lambda_a, \Lambda_v$ and
boundary conditions at the end nodes. To this end, define the set of
internal nodes $\mathcal{B} \subset \mathcal{V}$ as the set of nodes
that are connected to two or more edges and the set of end nodes as
$\mathcal{T}$, write $\hat{c}^i = \hat{c}|_{\Lambda^i}$, and let
$\mathcal{E}(y)$ denote the set of (one, two or three) edges in
$\{\Lambda^i\}$ sharing the node $y$. To impose continuity of the
concentrations, we set that the concentrations when viewed from each
edge must match at nodes:
\begin{equation}
  \hat{c}^i (y) = \hat{c}_y \qquad \foralls \Lambda^i \in \mathcal{E}(y),
  \quad \foralls y \in \mathcal{B} .
\end{equation}
Moreover, to ensure conservation of flux, we set that the flux going
in and out at nodes should add to zero, or more precisely, that for
each $y \in \mathcal{B}$:
\begin{equation}
  \sum_{i \in \mathcal{E}(y)}
  \left (\hat{D}^i A^i \partial_s \hat{c}^i (y) - A^i \hat u^i(y) \hat{c^i}(y) \right ) n_i(y)
  = 0
  \label{eq:flux_conservation}
\end{equation}
where the function $n_i : \mathcal{V} \rightarrow \{-1, 0, 1\}$
defines an orientation of each vertex relative to the
edges. Specifically, for an edge $\Lambda^i$ from $y_{\rm in}$ to $y_{\rm out}$
\begin{equation}
  n_i(y_{\rm in}) = 1, \quad
  n_i(y_{\rm{out}}) = -1, \quad
  n_i(y) = 0, \quad \forall y \in 
  \mathcal{V} \
  \,  \backslash \,  \{ y_{\rm in}, y_{\rm out} \}.  
\end{equation}

\mer{MER: Stopped here.}

%% For a given edge $\Lambda^i= (\mathsf{v}_\mathrm{in}^i, \mathsf{v}_{\mathrm{out}}^{i})$, we define the function $n_i: \mathcal{V} \rightarrow \{-1,0,1\}$ with $$
%% $$
%% The collection of bifurcation points is denoted by $\mathcal{B} = \{ \mathsf{v} \in \mathcal{V}, \,\,  \mathrm{card}(\mathcal{E}(\mathsf{v})) \geq  3\}$. For any $\mathsf{v} \in \mathcal{B}$, we have 
%% \begin{equation}
%% \sum_{ i \in \mathcal{E}(\mathsf{v})} (\hat D A_i \phi \partial_s \hat{u}_i(\mathsf{v})  -  A_i \hat u_i(\mathsf{v}) \hat c_i(\mathsf{v})) n_i(\mathsf{v}) = 0  \label{eq:flux_conservation}
%% \end{equation}

@@
